A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

In Section~\ref{section:svd}, fundamental mathematics of SVD and associated properties are presented. Then, the concept of spaces is explained to give the reader the understanding necessary to appreciate the transformations and projections involved in this work. Finally, Section~\ref{section:svd} describes model order space reduction for the permeability field within the principal component space. Section~\ref{section:model_simulation} starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to. A brief summary of the pre-processing step for each of the models is also presented. Section~\ref{section:results_discussion} provides the results and some discussion on the results of the simulations. It also gives further intepretation to the result obtained from the SVD upscaling technique. Finally, Section~\ref{section:conclusion} provides the conclusion.

>>>>

In Section~\ref{section:svd}, fundamental mathematics of SVD and associated properties are presented. Then, the concept of spaces is explained to give the reader the understanding necessary to appreciate the transformations and projections involved in this work. Finally, Section~\ref{section:svd} describes model order space reduction for the permeability field within the principal component space. Section~\ref{section:model_simulation} starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to. A brief summary of the pre-processing step for each of the models is also presented. Section~\ref{section:results_discussion} provides the results and further discussion on the results of the simulations, it also gives further interpretation to the result obtained from the SVD upscaling technique. Finally, Conclusions are drawn in Section~\ref{section:conclusion}.
